---
title: "AR Fire Fertilization — Corrections"
author: "Ian Klupar"
date: "9/27/2019"
output: html_document
---

```{r setup, echo=T, include=F, results='hide'}
knitr::opts_chunk$set(echo = TRUE)

# clear all
rm(list=ls())
if(!is.null(dev.list())) dev.off()
cat("\014")


# function for computing standard error
s.err <- function(x){
  sd(x)/sqrt(length(x))
}
```

```{r biomass, echo=T, include=F, results='hide'}
library(tidyverse)
library(modelr)
library(ggpubr)
library(broom)
options(na.action = na.warn)
```

####ANPP Species Corrections
***
***  
Fit a linear regression to an x~y relationship that I expect to be linear. For example: blades~litter in eriophorum. Next, determine which points are outside the 99% confidence interval for the regression. Next, remove those points, fit a new regression and then adjust the combined blades + litter biomass so it fits the appropriate relationship. I use y = mx + b and total = x + y to conserve biomass. Thus, x = (total - b)/(m + 1) and y = mx + b. 

```{r reset biomass}
biomass <- read.csv("/Users/ianklupar/Desktop/thesis-data/v2/organized/biomass/burn_fertilization_biomass.csv",
                    header = T, stringsAsFactors = F)
biomass <- as_tibble(biomass)
```

##### Corrections by species:
*Eriophorum vaginatum*
```{r biomass trial: erivag, echo=T, include=T, eval=F }
biomass %>% 
  ggplot(aes(x=ev.rhizome+ev.litter+ev.dead.sheath, y=ev.blade, color=site)) +
  geom_point(aes(shape=treatment)) +
  stat_smooth(method = "lm", size = 1, level = .99, se = F)+
  stat_regline_equation(aes(label = paste(..rr.label..)))
  
summary(lm(ev.blade~ev.rhizome+ev.litter+ev.dead.sheath, data = biomass))
```

```{r biomass corrections: erivag, echo=T, include=T, eval=T}
biomass %>% 
  do(augment(lm(ev.blade ~ ev.litter, data = .), data = .)) %>%
  mutate(group = as.numeric(abs(ev.blade - .fitted) < 2.58*.se.fit)) %>%   
  ggplot(aes(ev.litter, ev.blade)) + geom_point(aes(colour = factor(group)), size = 2) +
  stat_smooth(method = "lm", formula = y ~ x, size = 1, level = .99) +
  stat_regline_equation(aes(label = paste(..rr.label..)))+
  ggtitle("Eriophorum -- total")
  
biomass %>% 
  do(augment(lm(ev.blade ~ ev.litter, data = .), data = .)) %>%
  mutate(group = as.numeric(abs(ev.blade - .fitted) < 2.58*.se.fit)) %>% 
  filter(group==1) %>% 
  lm(ev.blade~ev.litter, data = .)
# regression: y = 0.75535 + 0.09058 * x is the regression for points inside the 99% CI 

x <- biomass %>%  
  do(augment(lm(ev.blade ~ ev.litter, data = .), data = .)) %>%
  mutate(group = as.numeric(abs(ev.blade - .fitted) < 2.58*.se.fit))

list <- which(x$group==0)
count <- 0

for(i in list){
      biomass[i,"ev.litter"] <- abs(((biomass[i,"ev.litter"]+biomass[i,"ev.blade"])-0.75535)/(0.09058+1))
      biomass[i,"ev.blade"] <- abs(0.75535 + (0.09058*biomass[i,"ev.litter"]))
      
      count <- count + 1
}

paste0("Number of corrected plots: ",count)

biomass %>% 
  ggplot(aes(ev.litter, ev.blade))+
  geom_point() +
  geom_smooth(method = stats::lm, se=F) +
  stat_regline_equation(aes(label = paste(..rr.label..)))

 rm(i, list, x)
```
  
*Petasites frigidus*

```{r biomass correction: petfri, echo=T, eval=T}

# S-B4-C high "pf.above" value
# remeasured weight using g = LAI/SLA; LAI=3.42, SLA(R.chamamourus)=0.01538

biomass[5,"pf.above"] <- 5.87 # was 11.577g
```

*Vaccinium vitis-idea*

```{r biomass correction: vacvit, echo=T, results='hide'}

biomass %>% 
  do(augment(lm(vv.newgrowth ~ vv.oldgrowth, data = .), data = .)) %>%
  mutate(group = as.numeric(abs(vv.newgrowth - .fitted) < 2.58*.se.fit)) %>%   
  ggplot(aes(vv.oldgrowth, vv.newgrowth)) + geom_point(aes(colour = factor(group)), size = 2) +
  stat_smooth(method = "lm", formula = y ~ x, size = 1, level = .99) +
  stat_regline_equation(aes(label = paste(..rr.label..)))+
  ggtitle("Vaccinium -- total")
  
biomass %>% 
  do(augment(lm(vv.newgrowth ~ vv.oldgrowth, data = .), data = .)) %>%
  mutate(group = as.numeric(abs(vv.newgrowth - .fitted) < 2.58*.se.fit)) %>% 
  filter(group==1 | vv.newgrowth < 2*vv.oldgrowth) %>% 
  lm(vv.newgrowth~vv.oldgrowth, data = .)

# y = 0.81239 + 0.05224 * x 
#  is the regression for points inside the 99% CI 

x <- biomass %>%  
  do(augment(lm(vv.newgrowth ~ vv.oldgrowth, data = .), data = .)) %>%
  mutate(group = as.numeric(abs(vv.newgrowth - .fitted) < 2.58*.se.fit))

list <- which(x$group==0)
count <- 0

for(i in list){
      biomass[i,"vv.oldgrowth"] <- abs((biomass[i,"vv.oldgrowth"]+biomass[i,"vv.newgrowth"])-0.81239)/(0.05224+1)
      biomass[i,"vv.newgrowth"] <- abs(0.81239 + 0.05224*biomass[i,"vv.oldgrowth"])
      
      count <- count + 1
}

paste0("Number of corrected plots: ",count)

biomass %>% 
  ggplot(aes(vv.oldgrowth, vv.newgrowth))+
  geom_point() +
  stat_regline_equation(aes(label = paste(..rr.label..))) +
  geom_smooth(method = stats::lm, se=F)

 rm(i, list, x, count)
```

*Ledum palustre*
 
```{r biomass correction: ledpal, echo=T, include=TRUE, results='hide'}
biomass <- biomass %>%
  mutate(lp.oldgrowth = (lp.oldgrowth.leaves + lp.oldgrowth.stems),
         lp.newgrowth = (lp.newgrowth.leaves + lp.newgrowth.stems))

biomass %>% 
  do(augment(lm(lp.newgrowth ~ lp.oldgrowth, data = .), data = .)) %>%
  mutate(group = as.numeric(abs(lp.newgrowth - .fitted) < 2.58*.se.fit)) %>%   
  ggplot(aes(lp.oldgrowth, lp.newgrowth)) + geom_point(aes(colour = factor(group)), size = 2) +
  stat_smooth(method = "lm", formula = y ~ x, size = 1, level = .99) +
  stat_regline_equation(aes(label = paste(..rr.label..)))+
  ggtitle("Ledum -- total")
  
biomass %>% 
  do(augment(lm(lp.newgrowth ~ lp.oldgrowth, data = .), data = .)) %>%
  mutate(group = as.numeric(abs(lp.newgrowth - .fitted) < 2.58*.se.fit)) %>% 
  filter(group==1) %>% 
  lm(lp.newgrowth~lp.oldgrowth, data = .)

# y = 3.32329 + 0.01526 * x 
#  is the regression for points inside the 99% CI 

x <- biomass %>%  
  do(augment(lm(lp.newgrowth ~ lp.oldgrowth, data = .), data = .)) %>%
  mutate(group = as.numeric(abs(lp.newgrowth - .fitted) < 2.58*.se.fit))

list <- which(x$group==0)
count <- 0

for(i in list){
      biomass[i,"lp.oldgrowth"] <- abs((biomass[i,"lp.oldgrowth"]+biomass[i,"lp.newgrowth"])-3.32329)/(0.01526+1)
      biomass[i,"lp.newgrowth"] <- abs(3.32329 + 0.01526*biomass[i,"lp.oldgrowth"])
      
      count <- count + 1
}

paste0("Number of corrected plots: ",count)

biomass %>% 
  ggplot(aes(lp.oldgrowth, lp.newgrowth))+
  geom_point() +
  stat_regline_equation(aes(label = paste(..rr.label..))) +
  geom_smooth(method = stats::lm, se=F)

 rm(i, list, x, count)
```
### End of corrections: first round!

```{r biomass scaling, echo=T, results='hide'}
biomass <- read.csv("/Users/ianklupar/Desktop/thesis-data/v2/organized/biomass/burn_fertilization_biomass.csv",
                    header = T, stringsAsFactors = F)
biomass <- as_tibble(biomass)

small_quad_spp <- c("ev.blade","ev.litter","ev.infl","ev.rhizome","ev.roots","ev.dead.sheath",
                    "ev.decomp.sheath","ev.tussockom","cb.blade","cb.litter","cb.sheath","cb.infl","cb.rhizome",
                    "cb.liveroots","cb.deadroots","vv.newgrowth","vv.oldgrowth","vv.infl","ct.newgrowth",
                    "ct.oldgrowth","ct.dead","ap.newgrowth","ap.oldgrowth","rc.above","rc.litter","rc.below",
                    "rc.infl","pf.above","pf.below","pf.litter","fine.roots","coarse.roots","moss","lichen",
                    "fungi","evergr.litter","decid.litter")

large_quad_spp <- c("bn.leaves","bn.newstem","bn.oldstem","bn.below","bn.infl","sp.newstem","sp.leaves",
                    "sp.oldstem","lp.newgrowth","lp.oldgrowth","lp.dead","lp.infl","lp.below")

biomass[small_quad_spp] <- select(biomass, small_quad_spp) * 25
biomass[large_quad_spp] <- select(biomass, large_quad_spp) * 4

biomass$treatment[biomass$treatment=="CX"] <- "C"

rm(small_quad_spp,large_quad_spp)

pft <- mutate(biomass, 
                   sedge.biomass = ev.blade + ev.rhizome + ev.infl + cb.blade + cb.rhizome + cb.infl,
                   decid.biomass = bn.leaves + bn.newstem + bn.oldstem + bn.infl + sp.leaves + sp.newstem +
                                   sp.oldstem,
                   evergr.biomass = vv.newgrowth + vv.oldgrowth + vv.infl + ct.newgrowth + ct.oldgrowth +
                                    lp.oldgrowth.leaves + lp.oldgrowth.stems + lp.newgrowth.stems +
                                    lp.infl + lp.dead + ap.newgrowth + ap.oldgrowth,
                   forb.biomass = rc.above + rc.litter + pf.above + pf.litter,
                   nonv.biomass = moss + lichen,
                   litter.biomass  = evergr.litter + decid.litter + rc.litter + pf.litter,
                   total.biomass = sedge.biomass + decid.biomass + evergr.biomass + forb.biomass,
              
                   sedge.anpp = ev.blade + ev.infl + cb.blade + cb.infl,
                   decid.anpp = bn.leaves + bn.newstem + bn.infl + sp.newstem + sp.leaves,
                   evergr.anpp = vv.newgrowth + vv.infl + lp.newgrowth.leaves + lp.infl + ct.newgrowth +
                                 ap.newgrowth,
                   forb.anpp = rc.above + rc.infl + pf.above,
                   total.anpp = sedge.anpp + decid.anpp + evergr.anpp + forb.anpp) %>% 
               select(site:treatment, sedge.biomass:total.anpp)

pft$site <- as.factor(pft$site)
pft$treatment <- as.factor(pft$treatment)
```

### ANOVA and Linear Model
```{r total anpp anova}
pft %>% filter() %>%
  aov(total.anpp ~ Error(block) + site*treatment, data = .) %>% 
  summary()
```

```{r total biomass anova}
pft %>% filter() %>%
  aov(total.biomass ~ Error(block) + site*treatment, data = .) %>% 
  summary()
```

```{r fang linear model}
model <- lm(total.anpp ~ site/as.factor(block)+treatment+site:treatment, data=pft)
summary(model)
```
  
#### Try with functional type anpp:biomass ratio
***
***
```{r}
biomass <- read.csv("/Users/ianklupar/Desktop/thesis-data/v2/organized/biomass/burn_fertilization_biomass.csv",
                    header = T, stringsAsFactors = F)
biomass <- as_tibble(biomass)
```

```{r complete biomass and productivity data}
pft <- mutate(biomass, 
                   sedge.biomass = ev.blade + ev.rhizome + ev.infl + cb.blade + cb.rhizome + cb.infl,
                   decid.biomass = bn.leaves + bn.newstem + bn.oldstem + bn.infl + sp.leaves + sp.newstem +
                                   sp.oldstem,
                   evergr.biomass = vv.newgrowth + vv.oldgrowth + vv.infl + ct.newgrowth + ct.oldgrowth +
                                    lp.oldgrowth.leaves + lp.oldgrowth.stems + lp.newgrowth.stems +
                                    lp.infl + lp.dead + ap.newgrowth + ap.oldgrowth,
                   forb.biomass = rc.above + rc.litter + pf.above + pf.litter,
                   nonv.biomass = moss + lichen,
                   litter.biomass  = evergr.litter + decid.litter + rc.litter + pf.litter,
                   total.biomass = sedge.biomass + decid.biomass + evergr.biomass + forb.biomass,
              
                   sedge.anpp = ev.blade + ev.infl + cb.blade + cb.infl,
                   decid.anpp = bn.leaves + bn.newstem + bn.infl + sp.newstem + sp.leaves,
                   evergr.anpp = vv.newgrowth + vv.infl + lp.newgrowth.leaves + lp.infl + ct.newgrowth +
                                 ap.newgrowth,
                   forb.anpp = rc.above + rc.infl + pf.above,
                   total.anpp = sedge.anpp + decid.anpp + evergr.anpp + forb.anpp) %>% 
               select(site:treatment, sedge.biomass:total.anpp)

pft$site <- as.factor(pft$site)
pft$treatment <- as.factor(pft$treatment)
```
### **ANPP PFT Corrections**
***
***  
```{r sedge corrections, echo=T, include=T, eval=F}
pft %>% 
  do(augment(lm(sedge.anpp ~ sedge.biomass, data = .), data = .)) %>%
  mutate(group = as.numeric(abs(sedge.anpp - .fitted) < 2.58*.se.fit)) %>%   
  ggplot(aes(sedge.biomass, sedge.anpp)) + 
  geom_point(aes(colour = factor(group)), size = 1.5) +
  stat_smooth(method = "lm", formula = y ~ x, size = 1, level = .99) +
  ggtitle("Sedge -- total")

pft %>% 
  do(augment(lm(sedge.anpp ~ sedge.biomass, data = .), data = .)) %>%
  mutate(group = as.numeric(abs(sedge.anpp - .fitted) < 2.58*.se.fit)) %>%   
  ggplot(aes(sedge.biomass, sedge.anpp, shape=site)) + 
  geom_point(aes(colour = factor(group)), size = 1.5) +
  stat_smooth(method = "lm", formula = y ~ x, size = 1, level = .99) +
  ggtitle("Sedge -- total")
```

```{r deciduous corrections, echo=T, include=T, eval=F}
pft %>% 
  do(augment(lm(decid.anpp ~ decid.biomass, data = .), data = .)) %>%
  mutate(group = as.numeric(abs(decid.anpp - .fitted) < 2.58*.se.fit)) %>%   
  ggplot(aes(decid.biomass, decid.anpp)) + 
  geom_point(aes(colour = factor(group)), size = 1.5) +
  stat_smooth(method = "lm", formula = y ~ x, size = 1, level = .99) +
  ggtitle("Decid -- total")

pft %>% 
  do(augment(lm(decid.anpp ~ decid.biomass, data = .), data = .)) %>%
  mutate(group = as.numeric(abs(decid.anpp - .fitted) < 2.58*.se.fit)) %>%   
  ggplot(aes(decid.biomass, decid.anpp, shape=site)) + 
  geom_point(aes(colour = factor(group)), size = 1.5) +
  stat_smooth(method = "lm", formula = y ~ x, size = 1, level = .99) +
  ggtitle("Decid -- total")
```

```{r evergreen corrections, echo=T, include=T, eva=F}
pft %>% 
  do(augment(lm(evergr.anpp ~ evergr.biomass, data = .), data = .)) %>%
  mutate(group = as.numeric(abs(evergr.anpp - .fitted) < 2.58*.se.fit)) %>%   
  ggplot(aes(evergr.biomass, evergr.anpp)) +
  geom_point(aes(colour = factor(group)), size = 1.5) +
  stat_smooth(method = "lm", formula = y ~ x, size = 1, level = .99) +
  ggtitle("Evergr -- total")

pft %>% 
  do(augment(lm(evergr.anpp ~ evergr.biomass, data = .), data = .)) %>%
  mutate(group = as.numeric(abs(evergr.anpp - .fitted) < 2.58*.se.fit)) %>%   
  ggplot(aes(evergr.biomass, evergr.anpp, shape=site)) +
  geom_point(aes(colour = factor(group)), size = 1.5) +
  stat_smooth(method = "lm", formula = y ~ x, size = 1, level = .99) +
  ggtitle("Evergr -- total")
```

```{r forb corrections, echo=T, include=T, eval=F}
pft %>% 
  do(augment(lm(forb.anpp ~ forb.biomass, data = .), data = .)) %>%
  mutate(group = as.numeric(abs(forb.anpp - .fitted) < 2.58*.se.fit)) %>%   
  ggplot(aes(forb.biomass, forb.anpp)) + 
  geom_point(aes(colour = factor(group)), size = 1.5) +
  stat_smooth(method = "lm", formula = y ~ x, size = 1, level = .99) +
  ggtitle("Forb -- total")

pft %>% 
  do(augment(lm(forb.anpp ~ forb.biomass, data = .), data = .)) %>%
  mutate(group = as.numeric(abs(forb.anpp - .fitted) < 2.58*.se.fit)) %>%   
  ggplot(aes(forb.biomass, forb.anpp, shape=site)) + 
  geom_point(aes(colour = factor(group)), size = 1.5) +
  stat_smooth(method = "lm", formula = y ~ x, size = 1, level = .99) +
  ggtitle("Forb -- total")
```

```{r plant functional type corrections, eval=F, include=F}
pft %>% 
  do(augment(lm(total.anpp ~ total.biomass, data = .), data = .)) %>%
  mutate(group = as.numeric(abs(total.anpp - .fitted) < 2.58*.se.fit)) %>%   
  ggplot(aes(total.biomass, total.anpp)) + 
  geom_point(aes(colour = factor(group)), size = 1.5) +
  stat_smooth(method = "lm", formula = y ~ x, size = 1, level = .99) +
  ggtitle("Combined -- total")

pft %>% 
  do(augment(lm(total.anpp ~ total.biomass, data = .), data = .)) %>%
  mutate(group = as.numeric(abs(total.anpp - .fitted) < 2.58*.se.fit)) %>%   
  ggplot(aes(total.biomass, total.anpp, shape=site)) + 
  geom_point(aes(colour = factor(group)), size = 1.5) +
  stat_smooth(method = "lm", formula = y ~ x, size = 1, level = .99) +
  ggtitle("Combined -- total")
```

```{r 2017 burn biomass, echo=T, eval=T, include=F}







```

  